Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-02-12 Ben_Manuscripts/thesis/structure_si.tex
starting dissertation

%\documentclass[journal=jpcbfk,manuscript=article]{achemso}
\documentclass{article}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}
\usepackage{array}
\usepackage{authblk}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}  
\renewcommand{\thetable}{S\arabic{table}}

%\SectionNumbersOn

\externaldocument[M-]{Final_Draft}

\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author[1]{Benjamin J. Coscia}
\author[2]{Joseph Yelk}
\author[2]{Matthew A. Glaser}
\author[1,3]{Douglas L. Gin}
\author[4]{Xunda Feng}
\author[1]{Michael R. Shirts*}
\date{E-mail: michael.shirts@colorado.edu}

\affil[1]{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\affil[2]{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
\affil[3]{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
\affil[4]{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}

\begin{document}

  \bibliographystyle{ieeetr}
  \graphicspath{{./supporting_figures/}}  % put all the figures here
  %\graphicspath{{./figures/}}
  \maketitle

  \section{Setup and analysis scripts}\label{section:python_scripts}

  All python and bash scripts used to set up systems and conduct post-simulation trajectory
  analysis, except for simulating X-ray diffraction (XRD) patterns, are available online at
  \texttt{https://github.com/bencoscia/llcsim}. Table~\ref{table:python_scripts} provides more 
  detail about specific scripts used for each type of analysis performed in the main text.

@@

  \section{Further details regarding monomer parameterization}\label{section:parameterization}

@@

	\item \textit{Anneal again to get final structure}: We repeated the
	same simulated annealing procedure using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from the
	last 10\% of the trajectory and was used to build all assemblies reported
	(Figure~\ref{fig:monomer}).

@@

  \begin{figure}[!htb]
	\centering
        \includegraphics[width=0.9\textwidth]{monomer.png}
	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
		the blue atom is sodium.}\label{fig:monomer}
  \end{figure}

@@

  \begin{table}[htb!]
  \centering
  \newcolumntype{A}{ >{\centering\arraybackslash} m{2.25in} }
  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.75in} }
  \newcolumntype{C}{m{3in}}
  \begin{tabular}{|A|B|C|}
  \hline
  \textbf{Script Name} & \textbf{Section} & ~~~~~~~~~~~~~~~~~~~~~\textbf{Description} \\
  \hline
  \texttt{/setup/param.sh} & \ref{M-method:parameterization} & Automatically run the monomer
  parameterization scheme outlined in Section~\ref{section:parameterization} given an initial
  structure file in .pdb format. \\ \hline

  \texttt{/setup/build.py} & \ref{M-method:unitcell_build} \& \ref{M-method:monomer_placement} &
  Build an initial configuration in the sandwiched or parallel displaced configuration with the 
  desired initial vertical monomer spacing, monomers-per-column, and columns-per-pore. \\ \hline

  \texttt{/setup/equil.sh} & \ref{M-section:equilibration} & Wrapper script for running the GROMACS 
  functions and python scripts needed in order to equilibrate an initial configuration. \\ \hline

  \texttt{/analysis/Structure\_char.py} & \ref{M-method:pore_spacing} & Calculate the distance 
  between pores. \\ \hline

  \texttt{/analysis/correlation.py} & \ref{M-section:correlation_length} & Calculate the 3D 
  correlation function from a trajectory and plot desired slices. \\ \hline

  \texttt{/analysis/regional\_density.py} & \ref{M-method:rdfs} & Calculate the density of a given
  monomer component as a function of its distance from the pore center. \\ \hline

  \texttt{/analysis/structure\_factor.py} & \ref{M-method:simple_systems} & Generate customizable
  trajectories of point scatterers, then calculate their structure factor and plot slices of it.
  \\ \hline

  \texttt{/analysis/disorder.py} & \ref{M-method:simple_systems} & Measure the magnitude of
  quenched disorder. \\ \hline

  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{M-method:ionic_conductivity} & Calculate the 
  ionic conductivity using the Nernst-Einsten relationship and collective diffusion model. \\ \hline

  \texttt{/setup/xlink.py} & \ref{M-method:xlink} & Iteratively cross-link a system given an 
  initial configuration. \\ \hline

  \texttt{/analysis/orientational\_order.py} & \ref{M-section:mon_per_pore} & Calculate the 
  nematic order parameter. \\ \hline

  \texttt{/analysis/tilt.py} & \ref{M-section:rspots} & Calculate the angle between the xy plane
  and the vector extending from the front to the back of each monomer tail. \\ \hline

  \texttt{/analysis/tail\_packing.py} & \ref{M-section:rspots} & Calculate the distribution of
  angles between the center of mass of each monomer tail and its nearest neighbor monomer tails.
  \\ \hline

  \texttt{/analysis/hexagonal\_packing.py} & \ref{M-section:rspots} & Calculate Fourier transform of
  2D array of hexagonal scatterers as shown in Figure~\ref{M-fig:hexagonal_ft} of the main text. \\ \hline

  \texttt{/analysis/compare\_disorder.py} & \ref{M-section:rpi} & Measure quenched disorder for
  each trajectory in an ensemble of simulations, then plot distributions of quenched disorder.
  \\ \hline

  \texttt{/analysis/hbonds\_pairing.py} & \ref{M-section:rdouble} & Identify all hydrogen bonds
  then count the number of monomer pairs that share hydrogen bonds. \\ \hline

  \texttt{/analysis/torsions.py} & \ref{M-section:slow_dynamics} & Calculate the autocorrelation
  function for a chosen dihedral. \\ \hline

@@

  \caption{The first column provides the names of the python scripts available in
  the \texttt{llcsim} GitHub repository that were used for system setup and post-simulation 
  trajectory analysis. Paths preceding script names are relative to the 
  \texttt{llcsim} root directory. The second columns lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{table:python_scripts}

@@

  \section{Attempted Self-assembly}\label{section:self_assembly}

  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{fig:isotropic_box}).
  The input file given to Packmol is shown below.

@@

  We use the nematic order parameter as defined in Section~\ref{method:nematic_order} to 
  observe any progress towards system ordering. In both cases, we see that the nematic
  order parameter stays close to zero for the duration of the simulation time, indicating
  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
  are slightly negative since there are only 400 monomers. 
  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
  proper choice of nematic director, measured values will range between 0 and 1. With a 
  large number of samples, an isotropic system would have an order parameter of 0.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{isotropic_box.png}
  \caption{}\label{fig:isotropic_box}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nematic_isotropic.png}
  \caption{}\label{fig:nematic_isotropic}
  \end{subfigure}
  \caption{(a) We created a box of isotropically packed monomers and allowed it to simulate
  for 100 ns using isotropic and anisotropic pressure coupling. (b) The nematic order 
  parameter hovers close to zero for the duration of the simulation meaning the system
  maintains its isotropic alignment.}\label{fig:self_assembly}
  \end{figure}

@@

  \section{Monomer build procedure}\label{section:monomer_build_procedure}

  Figure~\ref{fig:build_procedure} illustrates the procedure carried out by 
  \texttt{build.py} in order to build initial configurations.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{monomer_diagonal.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.42\textwidth}
  \includegraphics[width=\linewidth]{stacked_monomers.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.35\textwidth}
  \includegraphics[width=\linewidth]{initial_pore.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{initial_unit_cell.pdf}
  \caption{}
  \end{subfigure}
  %MRSF: I think this can be put in Supporting Information (we will get pushback to make this paper shorter, this is a good candidate)
  \caption{(a) We parameterized a single monomer and annealed it to produce a low-energy
		configuration. (b) We assembled monomers into columns by stacking them on top of each 
		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
  \end{figure}

  \section{Number of monomers per column}\label{section:monomers_per_column}

  We chose to build all systems using 20 monomers per column, i.e. for a simulation with 5 
  columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.  We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a smaller number of layers will cause the system to suffer from 
  larger finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (see
  Figure~\ref{fig:correlation}). The correlation function of the system which we
  built with 40 monomers per column is very similar to that created with 20 monomers
  per column (it continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. We do find that the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{z_correlation_overlay.png}
  \caption{}\label{fig:z_correlation_overlay}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{tall_correlation_full.png}
  \caption{}\label{fig:tall_correlation_full}
  \end{subfigure}
  \caption{(a) The correlation functions generated from ordered basin sandwiched 
  configurations are nearly the same when the $z$-dimension of the system is doubled.
  (b) Oscillations persist throughout the length of the correlation function for the
  sandwiched system in the ordered basin built with 40 monomers per column. The full
  system is ca. 17 nm tall so the full correlation function covers half this length
  since periodicity forces the remaining length to be its mirror image.}\label{fig:correlation_functions}
  \end{figure}

@@

  \section{Initial Configuration Dependence}\label{section:initial_config_dependence}

  We addressed any major dependence on initial configuration in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  columns per pore. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (see Figure~\ref{fig:stacking}). Our model is most consistent with experiment
  when built with 5 columns per pore, with monomers stacked 3.7 \AA~apart in 
  the parallel displaced configuration.

@@

  \subsection{Initial pore spacing}\label{section:initial_pore_spacing}

  We tested five different initial pore spacings, defined as the
  distance between the central axis of each pore with all others
  (Figure~\ref{fig:p2p_diagram}). To reduce the number of variables, we held the
  pore radius constant, at 5 \AA~and the distance between layers at 3.7 \AA~since
  those were the values used in our optimal system in the main text. We
  prioritized ensuring that resulting configurations maintain the expected
  hexagonal symmetry. If initial pore spacing is too small, we observe repulsion
  between columns which disrupts equilibration. If the pore spacing is too large
  the pores squeeze together, but in a distorted hexagonal array because the $xy$
  initial translation of the pores is somewhat erratic.

@@

	\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
	have a test system with an initial spacing below the experimental value. As soon
	as the restraining potential switches to 56 kJ mol$^{-1}$ nm$^{-2}$, the
	columns are able to repel resulting in a large jump in pore spacing
	(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
%		There is a large uncertainty in this value because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
%                towards cubic packing.

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
	it closely matches the experimental pore spacing. Again, we observe abrupt
	repulsion of columns once the restraining potential is switched to 56 kJ
	mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_41}). %After 400 ns, the
%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
%		spacings is 3.96 nm.

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10\% larger
	than the experimental value. This systems exhibits the smallest response to our 
 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
        value for all our simulations in the main text.
        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
	%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
	%pore spacing. We chose to use this value for all our simulations in the main
	%text.

	\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20\%
	larger than the experimental value. Once the restraining potential reaches 56
	kJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
	a linear trend (Figure~\ref{fig:p2p_50}).
%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
%		There is a large
 %               uncertainty with this value because, again, the array of pores deviates from 
 %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
   %             response.

	\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
	a distance where monomers in each pore no longer intersect those of adjacent pores. Once
	the restraining potential reaches 56 kJ mol$^{-1}$ nm$^{-2}$, the pore spacing
	changes erratically until it begins to settle when the force constants are
	below 3 kJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
	avoiding a system such as this where vacuum gaps between pore columns are
	introduced unnecessarily. 
	%The system equilibrates to a pore spacing of 4.27
    %$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
    %spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

  \item 8 \AA~: The largest pore radius that can achieved before
  energy minimization becomes problematic is 8 \AA. One should use caution with
  such a structure because of the relatively large vacuum space that is created
  in the pore region of the initial configuration. After being run through the
  full dry equilibration procedure, we see a combination of cylindrical and
  slit-like pores (Figure~\ref{fig:slits}). Measuring the pore radius of this
  system does not have a concrete meaning since slits do not have a single
  radius, but its calculated value is still reported in Table ~\ref{table:radii}. We
  are wary of such a non-symmetric structure and choose not to use a pore radius
  of 8 \AA~for our starting configurations.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \toprule
  Initial Pore Radius & Equilibrated Pore Radius \\
  \midrule
  2.5 \AA & $4.0 \pm 0.1$ \AA \\
  5 \AA   & $4.2 \pm 0.1$ \AA \\
  8 \AA   & $6.9 \pm 0.1$ \AA \\
  \bottomrule
  \end{tabular}
  \caption{The average pore radii of systems built with an initial pore
	  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
	  the pore radius is too large, slit pores may form.}~\label{table:radii}
  \end{table}

  \begin{figure}[!htb]
  \centering
  \begin{minipage}{0.475\textwidth}
  \centering
  \includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
  \caption{When creating an initial configuration, we define the pore radius,
  R, based on the distance of the carbonyl carbon from the pore's
  central axis.}~\label{fig:pore_radius_illustration}
  \end{minipage}\qquad
  \begin{minipage}{0.475\textwidth}
  \centering
  \vspace{4em}
  \includegraphics[width=\textwidth]{slit_pores.png}
  \vspace{1em}
  \caption{A system that was built with an initial pore radius of 8~\AA~equilibrates
  to a structure that exhibits both cylindrical and slit-like pores. As pictured 
  here, sodium ions are colored blue, carbon atoms in the aromatic ring of the head 
  group are colored orange and all else is colored cyan.}~\label{fig:slits}
  \end{minipage}
  \end{figure}

  \subsection{Initial stacking distance between monomers}\label{section:initial_dbwl}

@@

  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}

>>>>

\chapter{Test}

  \section{Setup and analysis scripts}\label{S-section:python_scripts_structure}

  All python and bash scripts used to set up systems and conduct post-simulation trajectory
  analysis, except for simulating X-ray diffraction (XRD) patterns, are available online at
  \texttt{https://github.com/bencoscia/llcsim}. Table~\ref{S-table:python_scripts_structure} provides more 
  detail about specific scripts used for each type of analysis performed in the main text.

@@

  \section{Further details regarding monomer parameterization}\label{S-section:parameterization}

@@

	\item \textit{Anneal again to get final structure}: We repeated the
	same simulated annealing procedure using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from the
	last 10\% of the trajectory and was used to build all assemblies reported
	(Figure~\ref{S-fig:monomer}).

@@

  \begin{figure}[!htb]
	\centering
        \includegraphics[width=0.9\textwidth]{monomer.png}
	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
		the blue atom is sodium.}\label{S-fig:monomer}
  \end{figure}

@@

  \begin{table}[htb!]
  \centering
  \newcolumntype{A}{ >{\centering\arraybackslash} m{2.25in} }
  \newcolumntype{B}{ >{\centering\arraybackslash} m{0.75in} }
  \newcolumntype{C}{m{3in}}
  \begin{tabular}{|A|B|C|}
  \hline
  \textbf{Script Name} & \textbf{Section} & ~~~~~~~~~~~~~~~~~~~~~\textbf{Description} \\
  \hline
  \texttt{/setup/param.sh} & \ref{method:parameterization} & Automatically run the monomer
  parameterization scheme outlined in Section~\ref{S-section:parameterization} given an initial
  structure file in .pdb format. \\ \hline

  \texttt{/setup/build.py} & \ref{method:unitcell_build} \& \ref{method:monomer_placement} &
  Build an initial configuration in the sandwiched or parallel displaced configuration with the 
  desired initial vertical monomer spacing, monomers-per-column, and columns-per-pore. \\ \hline

  \texttt{/setup/equil.sh} & \ref{section:equilibration} & Wrapper script for running the GROMACS 
  functions and python scripts needed in order to equilibrate an initial configuration. \\ \hline

  \texttt{/analysis/Structure\_char.py} & \ref{method:pore_spacing} & Calculate the distance 
  between pores. \\ \hline

  \texttt{/analysis/correlation.py} & \ref{section:correlation_length} & Calculate the 3D 
  correlation function from a trajectory and plot desired slices. \\ \hline

  \texttt{/analysis/regional\_density.py} & \ref{method:rdfs} & Calculate the density of a given
  monomer component as a function of its distance from the pore center. \\ \hline

  \texttt{/analysis/structure\_factor.py} & \ref{method:simple_systems} & Generate customizable
  trajectories of point scatterers, then calculate their structure factor and plot slices of it.
  \\ \hline

  \texttt{/analysis/disorder.py} & \ref{method:simple_systems} & Measure the magnitude of
  quenched disorder. \\ \hline

  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{method:ionic_conductivity} & Calculate the 
  ionic conductivity using the Nernst-Einsten relationship and collective diffusion model. \\ \hline

  \texttt{/setup/xlink.py} & \ref{method:xlink} & Iteratively cross-link a system given an 
  initial configuration. \\ \hline

  \texttt{/analysis/orientational\_order.py} & \ref{section:mon_per_pore} & Calculate the 
  nematic order parameter. \\ \hline

  \texttt{/analysis/tilt.py} & \ref{section:rspots} & Calculate the angle between the xy plane
  and the vector extending from the front to the back of each monomer tail. \\ \hline

  \texttt{/analysis/tail\_packing.py} & \ref{section:rspots} & Calculate the distribution of
  angles between the center of mass of each monomer tail and its nearest neighbor monomer tails.
  \\ \hline

  \texttt{/analysis/hexagonal\_packing.py} & \ref{section:rspots} & Calculate Fourier transform of
  2D array of hexagonal scatterers as shown in Figure~\ref{fig:hexagonal_ft} of the main text. \\ \hline

  \texttt{/analysis/compare\_disorder.py} & \ref{section:rpi} & Measure quenched disorder for
  each trajectory in an ensemble of simulations, then plot distributions of quenched disorder.
  \\ \hline

  \texttt{/analysis/hbonds\_pairing.py} & \ref{section:rdouble} & Identify all hydrogen bonds
  then count the number of monomer pairs that share hydrogen bonds. \\ \hline

  \texttt{/analysis/torsions.py} & \ref{section:slow_dynamics} & Calculate the autocorrelation
  function for a chosen dihedral. \\ \hline

@@

  \caption{The first column provides the names of the python scripts available in
  the \texttt{llcsim} GitHub repository that were used for system setup and post-simulation 
  trajectory analysis. Paths preceding script names are relative to the 
  \texttt{llcsim} root directory. The second columns lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{S-table:python_scripts_structure}

@@

  \section{Attempted Self-assembly}\label{S-section:self_assembly}

  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{S-fig:isotropic_box}).
  The input file given to Packmol is shown below.

@@

  We use the nematic order parameter as defined in Section~\ref{S-method:nematic_order} to 
  observe any progress towards system ordering. In both cases, we see that the nematic
  order parameter stays close to zero for the duration of the simulation time, indicating
  an isotropic arrangement of head groups (Figure~\ref{S-fig:nematic_isotropic}). The values
  are slightly negative since there are only 400 monomers. 
  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
  proper choice of nematic director, measured values will range between 0 and 1. With a 
  large number of samples, an isotropic system would have an order parameter of 0.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{isotropic_box.png}
  \caption{}\label{S-fig:isotropic_box}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nematic_isotropic.png}
  \caption{}\label{S-fig:nematic_isotropic}
  \end{subfigure}
  \caption{(a) We created a box of isotropically packed monomers and allowed it to simulate
  for 100 ns using isotropic and anisotropic pressure coupling. (b) The nematic order 
  parameter hovers close to zero for the duration of the simulation meaning the system
  maintains its isotropic alignment.}\label{S-fig:self_assembly}
  \end{figure}

@@

  \section{Monomer build procedure}\label{S-section:monomer_build_procedure}

  Figure~\ref{S-fig:build_procedure} illustrates the procedure carried out by 
  \texttt{build.py} in order to build initial configurations.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{monomer_diagonal.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.42\textwidth}
  \includegraphics[width=\linewidth]{stacked_monomers.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.35\textwidth}
  \includegraphics[width=\linewidth]{initial_pore.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{initial_unit_cell.pdf}
  \caption{}
  \end{subfigure}
  %MRSF: I think this can be put in Supporting Information (we will get pushback to make this paper shorter, this is a good candidate)
  \caption{(a) We parameterized a single monomer and annealed it to produce a low-energy
		configuration. (b) We assembled monomers into columns by stacking them on top of each 
		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{S-fig:build_procedure}
  \end{figure}

  \section{Number of monomers per column}\label{S-section:monomers_per_column}

  We chose to build all systems using 20 monomers per column, i.e. for a simulation with 5 
  columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.  We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a smaller number of layers will cause the system to suffer from 
  larger finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (see
  Figure~\ref{S-fig:correlation}). The correlation function of the system which we
  built with 40 monomers per column is very similar to that created with 20 monomers
  per column (it continues to oscillate for its full length
  (Figure~\ref{S-fig:tall_correlation_full})). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. We do find that the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{z_correlation_overlay.png}
  \caption{}\label{S-fig:z_correlation_overlay}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{tall_correlation_full.png}
  \caption{}\label{S-fig:tall_correlation_full}
  \end{subfigure}
  \caption{(a) The correlation functions generated from ordered basin sandwiched 
  configurations are nearly the same when the $z$-dimension of the system is doubled.
  (b) Oscillations persist throughout the length of the correlation function for the
  sandwiched system in the ordered basin built with 40 monomers per column. The full
  system is ca. 17 nm tall so the full correlation function covers half this length
  since periodicity forces the remaining length to be its mirror image.}\label{S-fig:correlation_functions}
  \end{figure}

@@

  \section{Initial Configuration Dependence}\label{S-section:initial_config_dependence}

  We addressed any major dependence on initial configuration in the main text.
  There we showed that systems are stable when made with 4, 5, 6, 7, and 8
  columns per pore. We also showed that systems are stable when monomer head
  groups are oriented in the parallel displaced and sandwiched configurations
  (see Figure~\ref{S-fig:stacking}). Our model is most consistent with experiment
  when built with 5 columns per pore, with monomers stacked 3.7 \AA~apart in 
  the parallel displaced configuration.

@@

  \subsection{Initial pore spacing}\label{S-section:initial_pore_spacing}

  We tested five different initial pore spacings, defined as the
  distance between the central axis of each pore with all others
  (Figure~\ref{S-fig:p2p_diagram}). To reduce the number of variables, we held the
  pore radius constant, at 5 \AA~and the distance between layers at 3.7 \AA~since
  those were the values used in our optimal system in the main text. We
  prioritized ensuring that resulting configurations maintain the expected
  hexagonal symmetry. If initial pore spacing is too small, we observe repulsion
  between columns which disrupts equilibration. If the pore spacing is too large
  the pores squeeze together, but in a distorted hexagonal array because the $xy$
  initial translation of the pores is somewhat erratic.

@@

	\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
	have a test system with an initial spacing below the experimental value. As soon
	as the restraining potential switches to 56 kJ mol$^{-1}$ nm$^{-2}$, the
	columns are able to repel resulting in a large jump in pore spacing
	(Figure~\ref{S-fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
%		There is a large uncertainty in this value because the 1-4 pore spacing
%		(Figure~\ref{S-fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
%                towards cubic packing.

		\item 41 \AA~: We chose to test a pore spacing of 41 \AA~since
	it closely matches the experimental pore spacing. Again, we observe abrupt
	repulsion of columns once the restraining potential is switched to 56 kJ
	mol$^{-1}$ nm$^{-2}$ (Figure~\ref{S-fig:p2p_41}). %After 400 ns, the
%		average pore spacing settles below the experimental value at 4.07 $\pm$ 0.21
%		nm. Again, a large uncertainty in this value occurs because the 1-4 pore spacing
%		(Figure~\ref{S-fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.44 nm while the average of all other pore
%		spacings is 3.96 nm.

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10\% larger
	than the experimental value. This systems exhibits the smallest response to our 
 		equilibration procedure (Figure~\ref{S-fig:p2p_45}) and we chose to use this
        value for all our simulations in the main text.
        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
	%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
	%pore spacing. We chose to use this value for all our simulations in the main
	%text.

	\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20\%
	larger than the experimental value. Once the restraining potential reaches 56
	kJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
	a linear trend (Figure~\ref{S-fig:p2p_50}).
%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
%		There is a large
 %               uncertainty with this value because, again, the array of pores deviates from 
 %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
   %             response.

	\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
	a distance where monomers in each pore no longer intersect those of adjacent pores. Once
	the restraining potential reaches 56 kJ mol$^{-1}$ nm$^{-2}$, the pore spacing
	changes erratically until it begins to settle when the force constants are
	below 3 kJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{S-fig:p2p_55}). We recommend
	avoiding a system such as this where vacuum gaps between pore columns are
	introduced unnecessarily. 
	%The system equilibrates to a pore spacing of 4.27
    %$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
    %spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

  \item 8 \AA~: The largest pore radius that can achieved before
  energy minimization becomes problematic is 8 \AA. One should use caution with
  such a structure because of the relatively large vacuum space that is created
  in the pore region of the initial configuration. After being run through the
  full dry equilibration procedure, we see a combination of cylindrical and
  slit-like pores (Figure~\ref{S-fig:slits}). Measuring the pore radius of this
  system does not have a concrete meaning since slits do not have a single
  radius, but its calculated value is still reported in Table ~\ref{S-table:radii}. We
  are wary of such a non-symmetric structure and choose not to use a pore radius
  of 8 \AA~for our starting configurations.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \hline
  Initial Pore Radius & Equilibrated Pore Radius \\
  \hline
  2.5 \AA & $4.0 \pm 0.1$ \AA \\
  5 \AA   & $4.2 \pm 0.1$ \AA \\
  8 \AA   & $6.9 \pm 0.1$ \AA \\
  \hline
  \end{tabular}
  \caption{The average pore radii of systems built with an initial pore
	  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
	  the pore radius is too large, slit pores may form.}~\label{S-table:radii}
  \end{table}

  \begin{figure}[!htb]
  \centering
  \begin{minipage}{0.475\textwidth}
  \centering
  \includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
  \caption{When creating an initial configuration, we define the pore radius,
  R, based on the distance of the carbonyl carbon from the pore's
  central axis.}~\label{S-fig:pore_radius_illustration}
  \end{minipage}\qquad
  \begin{minipage}{0.475\textwidth}
  \centering
  \vspace{4em}
  \includegraphics[width=\textwidth]{slit_pores.png}
  \vspace{1em}
  \caption{A system that was built with an initial pore radius of 8~\AA~equilibrates
  to a structure that exhibits both cylindrical and slit-like pores. As pictured 
  here, sodium ions are colored blue, carbon atoms in the aromatic ring of the head 
  group are colored orange and all else is colored cyan.}~\label{S-fig:slits}
  \end{minipage}
  \end{figure}

  \subsection{Initial stacking distance between monomers}\label{S-section:initial_dbwl}

@@

  \section{Calculation of pore-to-pore spacing statistics}\label{S-section:p2p_stats}
